---
layout: "post"
title: "Bath Air Quality Report -- London Road AURN"
output: html_document
---

# Bath Air Quality Report -- London Road AURN (`r paste(dates, collapse="-")`)

The report shows levels of nitrogen-oxide pollutants for the period `r paste(dates, collapse="-")`. The report 
used data from the London Road AURN site.

## Wind Speeds and Direction

The following diagram, known as a *wind rose* plots the frequency of wind speed/direction frequencies. Longer slices indicate 
directions from which stronger winds are more frequently found. The slices are colour coded based on the wind strength.

```{r echo=FALSE, fig.retina=2, dpi=120}
windRose(londonRd, paddle=FALSE, main="Wind Rose from London Road AURN")
```

The following diagram shows the same information, but broken out by season of the year.

```{r echo=FALSE, fig.retina=2, dpi=120}
windRose(londonRd, paddle=FALSE, main="Seasonal Wind Rose from London Road AURN", type="season")
```

>**Insight**: The prevailing winds in Bath are from the west and south-west. However earlier in the year, winds are more often found from an easterly direction.

## Pollution Times

Levels of pollutants often vary with the time of day, week and season. This is particularly true for man-made 
pollutants. The following diagrams show this information from a number of perspectives.

### How do pollutant levels vary by time of day?

```{r echo=FALSE, fig.retina=2, dpi=120}
timeVariation(londonRd, main="Variation of NOx levels by time of day")
```

>**Insight**: Nitrogen levels in Bath are highest at early morning and late afternoon. Levels are highest 
in the week and lower at weekends.

The following calendar views show which days of the year had the highest levels of Nitrogen-Oxides for 
the start and end of the reporting period.

```{r echo=FALSE, fig.retina=2, dpi=120}
calendarPlot(londonRd, main=paste("Calendar view of NOx levels for ", from), year=to)
```

```{r echo=FALSE, fig.retina=2, dpi=120}
calendarPlot(londonRd, main=paste("Calendar view of NOx levels for ", to), year=to)
```

## Pollution Levels

What are the trends in pollutants during the reporting period?

The following chart shows the average weekly nitrogen oxide pollutant levels.

```{r echo=FALSE, fig.retina=2, dpi=120}
timePlot(londonRd, pollutant=c("nox", "no2", "no"), avg.time="month", smooth=TRUE, main="Average weekly pollutant levels")
```

To better highlight the general trends the following chart normalises the average annual figures using ```r from` as a baseline year.

```{r echo=FALSE, fig.retina=2, dpi=120}
timePlot(londonRd, pollutant=c("nox", "no2", "no"), avg.time="year", smooth=TRUE, main="Normalised average annual pollutant levels", normalise=paste("1/1/", from, sep=""))
```

>**Insight**: the general trend for nitrogen oxides is dropping

## Effect of Wind on Pollution

The following *pollution rose* shows the effect of wind speed and direction on nitrogen-oxide pollution.

```{r echo=FALSE}
percentileRose(londonRd, smooth=TRUE)
```

The diagram is broken down by season to look for seasonal influences

```{r echo=FALSE}
 percentileRose(londonRd, smooth=TRUE, type="season")
```

>**Insight**: there doesn't appear to be any major contribution from wind speed.
